ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-09-26 rebuttal.tex

\textbf{Our response:}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Reviewer \#2:}

\textit{My main concern with the creation of a publically available database, formatted with ChemKED, is that it seems that the creation of the files has to be done manually, i.e. susceptible for errors. This is especially true if the experiment comprises a big set of datapoints and/or hundreds of measured species. Furthermore, the YAML data serialization format is indeed human-readable, but it does not provide an easy summary/overview of the experimental data, such as an excel or CSV file would give, and therefore, people might be not willing to put the extra effort.}

\textbf{Reviewer comment:}
\textit{1.~How are the authors planning on `forcing' the experimentalists to publish their data in this new ChemKED file format?}

\textbf{Our response:}
While we cannot force anyone to use a particular format, we hope that by defining a format and ecosystem with desirable features---including inherent openness and usability---experimentalists will begin adopting a community-standard format. In fact, we have already received interest from various groups, and hope this will grow as we continue to improve and add features. We also hope that at a certain point, with wide adoption, sharing experimental data in a standard format will become the expected norm (e.g., when submitting an article for publication) like sharing a Chemkin-format chemical kinetic model.

@@

\textit{2.~Am I correct to state that ChemKED is a YAML file with a predefined structure?}

\textbf{Our response:}
Yes, ChemKED files are files in YAML format, with a prescribed structure and set of contents.

### 2017-09-26 pyked.tex
fixed sentence in response to #3

We therefore believe there remains a need for an open, community-focused and
developed, combustion\slash chemical kinetics data format. In this work, we
present a new, open-source, human- and machine-readable data standard for
fundamental combustion experiments, \ck{}, and offer tools for easily working
with data encoded in this format. Niemeyer recently introduced an initial
version of the \ck{} format~\autocite{Niemeyer:2016wf}, and in this work we
further formalize and develop the standard. We also discuss a related Python
software tool for validating and working with \ck{} files: \pk{}. Our
motivations are similar those of the PrIMe and ReSpecTh teams: the \ck{} project
will enable easy sharing and use of fundamental combustion data, for the
(primary) purposes of developing and validating predictive chemical kinetic
models. However, we make usability a major design focus, and plan to share all
data and software openly to cultivate a community of user-contributors.

>>>>

We therefore believe there remains a need for an open, community-focused and
developed, combustion\slash chemical kinetics data format. In this work, we
present a new, open-source, human- and machine-readable data standard for
fundamental combustion experiments, \ck{}, and offer tools for easily working
with data encoded in this format. Niemeyer recently introduced an initial
version of the \ck{} format~\autocite{Niemeyer:2016wf}, and in this work we
further formalize and develop the standard. We also discuss a related Python
software tool for validating and working with \ck{} files: \pk{}. Our
motivations resemble those of the PrIMe and ReSpecTh teams: the \ck{} project
will enable easy sharing and use of fundamental combustion data, for the
(primary) purposes of developing and validating predictive chemical kinetic
models. However, we make usability a major design focus, and plan to share all
data and software openly to cultivate a community of user-contributors.
